Future Evolution of CSMA Protocols for the IEEE 802.11 Standard

### 2013-02-28 paper.tex
future work

>>>>

\section{Future Work}

In this workshop paper, we have evaluated the protocols under discussion in a very simple scenario using ideal channel, ideal clocks and saturation conditions.
Furthermore, all the participating stations use the same protocol and have a single traffic  class.
The presented metrics include only throughput and fairness, whereas delay, jitter and packet have been omitted.
Another scenario of interest that we have not included is the situation in which the stations join the contention to transmit a file and then they leave.

Our proposed protocol is based on CSMA/ECA, which works well in non-ideal conditions, and the results we are currently obtaining confirm that CSMA/ECA with hysteresis and fair-share inherits the flexibility and robustness of its predecessors.

Regarding the implementation in real prototypes, it has been proven difficult until now, as the protocols are embedded in the networks interfaces and it is not possible to reprogram them.
There are current advances in that direction \cite{tinnirello2012wmp} but it is still difficult to set the backoff to a deterministic value after successful transmissions in available hardware.

Our intention is to try our protocols in a different technology, namely radio-frequency identification (RFID), where there is programmable hardware that can be used to implement arbitrary protocols.
RFID uses also a contention protocol which are prone to collisions, and we believe it can be a first area in which we will be available to develop working prototypes to validate some of the ideas proposed in the present paper.
